\section{﻿Lasagne}


\paragraph{Ingredienser hvit saus ala Gordon Ramsey}
\begin{itemize}[noitemsep]
	\item 25 gram butter
	\item 25 gram flour
	\item 300 ml milk
	\item Pinch of ground nutmeg
	\item 60 gram cheddar cheese, grated
	\item 30 gram parmesan cheese, grated
	\item 6 sheets of `non--cook' lasagne sheets
\end{itemize}

\paragraph{Ingredienser tomatsaus ala Klikk}
\begin{itemize}[noitemsep]
	\item 1 stk tomatbokser eller tre ferske tomater
	\item 2 ss kyllingbuljong
	\item 2 stk soltørkede tomater
	\item 1 ts sukker
	\item 1 ts hvitvinseddik eller eple-eddik
	\item 1 stk laurbærblad
	\item 1 ts oregano (eller timian, merian, basilikum, estragon eller salvie)
	\item  $\frac{1}{2}$  ts anisfrø
	\item olje til steking
	\item salt og pepper
\end{itemize}

\paragraph{Framgangsmåte rød saus}
\begin{enumerate}[noitemsep]
	\item Ha i tomatboksen, kyllingbuljong, finhakkede soltørkede tomater, sukker, eddik og laurbærblad.
	\item Knus oregano (eller andre urter) og anisfrø i en morter (du kan droppe dette, men da blir aromaene mer dempet).
	\item Ha i kjelen. Smak til med salt og pepper.
	\item Juster også sukker/eddik etter smak.
	\item La det koke i minst 7--8 minutter.
	\item Sausen kan også koke i mye lenger på svak varme.
	\end{enumerate}

	\paragraph{Framgangsmåte hvit}
	\begin{enumerate}[noitemsep]
	\item To make the cheese sauce, first melt the butter in a saucepan.
	\item Add the flour and using a wooden spoon, stir to form a paste.
	\item Over a gentle heat add a third of the milk, whisking to prevent any lumps forming.
	\item Add the rest of the milk a third at a time, whisking as you go.
	\item Season with salt and pepper and a pinch of ground nutmeg.
	\item Allow the sauce to cook out for another minute before adding the Cheddar cheese.
	\item Stir and remove from the heat.
	\item Spoon half of the meat sauce into the bottom of the baking dish and place pasta sheets on top (break the sheets if necessary to avoid any overlapping).
	\item Next, pour in just under half of the cheese sauce, and spread evenly using a spatula before spooning the remaining meat on top.
	\item Add the final layer of pasta and use the spatula to pour over the remaining cheese sauce.
	\item Finish with the grated Parmesan and sprinkle with another pinch of oregano.
	\item Add a light seasoning of salt and pepper before cleaning the edges of the dish and placing in the oven to bake for 20--25 minutes, or until golden brown.
\end{enumerate}


Kilde: Gordon Ramsay for hvit saus. Klikk.no for tomatsausen
